### 2018-11-07 Sections/QTCP_protocol_stack.tex
More indexing

The structure of the protocol stack for QTCP is shown in Fig.~\ref{fig:stack}. In summary, the layers in the protocol stack are, beginning from the lowest level:
\begin{itemize}
\item \textsc{Data (Message)}\index{Data (message) layer}: Raw data (`payload') Alice wishes to transmit to Bob. Comprises both \textsc{Quantum Data}\index{Quantum data layer} and \textsc{Classical Data}\index{Classical data layer}.
\item \textsc{Packet}\index{Packet layer}: Decomposition of \textsc{Data} into blocks (\textsc{Packet Data}\index{Packet data layer}), and associated classical \textsc{Packet Headers}\index{Packet header layer} containing metadata (e.g routing information).
\item \textsc{Strategy}\index{Strategy layer}: Construct \textsc{Packet} routing strategies based on a cost optimisation algorithm.
\item \textsc{Transport}\index{Transport layer}: Physical routing of \textsc{Packets} to arrive at their destination, based upon metadata contained in \textsc{Packet Header}. Perform collision detection during transit.
\item \textsc{Reconstruction}\index{Reconstruction layer}: Reconstruct \textsc{Data} from received \textsc{Packets}.
\item \textsc{Quality of Service (QoS)}\index{Quality of service (QoS) layer}: Apply QEC and determine whether \textsc{QoS} requirements have been satisfied.
\item \textsc{Services \& Applications}\index{Services \& applications layer}: High-level interface to \textsc{Data} presented to Bob's services and applications. The interface abstracts away lower levels of the protocol stack, presenting Bob with only \textsc{Data} and its associated metadata.
\end{itemize}

@@

\subsubsection{Packet} \label{sec:packet_layer} \index{Packet layer}

@@

\paragraph{Packet data} \index{Packet data layer}

@@

\paragraph{Packet header} \label{sec:packet_header} \index{Packet header layer}

>>>>

The structure of the protocol stack for QTCP is shown in Fig.~\ref{fig:stack}. In summary, the layers in the protocol stack are, beginning from the lowest level:
\begin{itemize}
\item \textsc{Data (Message)}\index{Data (message) layer}: Raw data (`payload') Alice wishes to transmit to Bob. Comprises both \textsc{Quantum Data}\index{Quantum data layer} and \textsc{Classical Data}\index{Classical data layer}.
\item \textsc{Packet}\index{Packet!Layer}: Decomposition of \textsc{Data} into blocks (\textsc{Packet Data}\index{Packet!Data layer}), and associated classical \textsc{Packet Headers}\index{Packet!Header layer} containing metadata (e.g routing information).
\item \textsc{Strategy}\index{Strategy layer}: Construct \textsc{Packet} routing strategies based on a cost optimisation algorithm.
\item \textsc{Transport}\index{Transport layer}: Physical routing of \textsc{Packets} to arrive at their destination, based upon metadata contained in \textsc{Packet Header}. Perform collision detection during transit.
\item \textsc{Reconstruction}\index{Reconstruction layer}: Reconstruct \textsc{Data} from received \textsc{Packets}.
\item \textsc{Quality of Service (QoS)}\index{Quality of service (QoS) layer}: Apply QEC and determine whether \textsc{QoS} requirements have been satisfied.
\item \textsc{Services \& Applications}\index{Services \& applications layer}: High-level interface to \textsc{Data} presented to Bob's services and applications. The interface abstracts away lower levels of the protocol stack, presenting Bob with only \textsc{Data} and its associated metadata.
\end{itemize}

@@

\subsubsection{Packet} \label{sec:packet_layer} \index{Packet!Layer}

@@

\paragraph{Packet data} \index{Packet!Data layer}

@@

\paragraph{Packet header} \label{sec:packet_header} \index{Packet!Header layer}

### 2018-11-07 Sections/classical_networking_protocols.tex
More indexing

\dropcap{T}{here} have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet-switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collisions!Detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsection{Network hierarchies} \index{Network hierarchies}

>>>>

\dropcap{T}{here} have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet!Switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collisions!Detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsection{Network hierarchies} \index{Network!Hierarchies}

### 2018-11-07 Sections/cloud_quantum_computing.tex
More indexing

\subsection{Outsourced quantum computation} \index{Outsourced quantum computation}

@@

Classically, there are two main models for how a distributed computation may proceed -- in \textit{parallel}\index{Parallel computation}, or in \textit{series}\index{Series computation} -- whereby sub-algorithms are performed either side-by-side simultaneously, or one after another in a pipeline. The two models are illustrated in Fig.~\ref{fig:distributed}.

@@

\subsection{Outsourced quantum research} \index{Outsourced quantum research}\index{Fundamental physics experiments}

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing\index{Outsourced quantum technology}. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research\index{Basic science research}, or perform precise quantum metrology.

@@

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols\index{Outsourced protocols}\index{Delegated protocols} using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

@@

Examples of how this type of model might be applied could include, but not be limited to research into:
\begin{itemize}
	\item Quantum information processing protocols, beyond only quantum computation, bits and qubits.
	\item Bose-Einstein condensates (BECs)\index{Bose-Einstein condensates (BECs)}.
	\item Light-matter interactions.\index{Light-matter!Interactions}
	\item Quantum thermodynamics and quantum statistical mechanics.\index{Quantum thermodynamics}\index{Quantum statistical mechanics}
	\item Quantum phase-transitions.\index{Quantum phase-transitions}
	\item Quantum optics, involving all manner of quantum states of light, beyond only those raised in Sec.~\ref{sec:opt_enc_of_qi}.\index{Quantum optics}
	\item Optical interferometry.\index{Optical interferometry}
	\item Providing a practical platform for university teaching and education.
\end{itemize}

>>>>

\subsection{Outsourced quantum computation} \index{Outsourced!Quantum computation}

@@

Classically, there are two main models for how a distributed computation may proceed -- in \textit{parallel}\index{Parallel!Computation}, or in \textit{series}\index{Series computation} -- whereby sub-algorithms are performed either side-by-side simultaneously, or one after another in a pipeline. The two models are illustrated in Fig.~\ref{fig:distributed}.

@@

\subsection{Outsourced quantum research} \index{Outsourced!Quantum research}\index{Fundamental physics experiments}

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing\index{Outsourced!Quantum technology}. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research\index{Basic science research}, or perform precise quantum metrology.

@@

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols\index{Outsourced!Protocols}\index{Delegated protocols} using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

@@

Examples of how this type of model might be applied could include, but not be limited to research into:
\begin{itemize}
	\item Quantum information processing protocols, beyond only quantum computation, bits and qubits.
	\item Bose-Einstein condensates (BECs)\index{Bose-Einstein condensates (BECs)}.
	\item Light-matter interactions.\index{Light-matter!Interactions}
	\item Quantum thermodynamics and quantum statistical mechanics.\index{Quantum thermodynamics}\index{Quantum statistical mechanics}
	\item Quantum phase-transitions.\index{Quantum phase-transitions}
	\item Quantum optics, involving all manner of quantum states of light, beyond only those raised in Sec.~\ref{sec:opt_enc_of_qi}.\index{Quantum optics}
	\item Optical interferometry.\index{Optical!Interferometry}
	\item Providing a practical platform for university teaching and education.
\end{itemize}

### 2018-11-07 Sections/cryptowars.tex
More indexing

\subsection{Private-key cryptography}\index{Private-key cryptography}

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key cryptography}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private-key lengths will need to be doubled to maintain an equivalent level of security against brute-force attacks.

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number splitting attack}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Intercept-resend attacks}, but not of an intercept-resend\index{Intercept-resend attacks} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis, thereby recovering the associated secret-key bit.

@@

What would be more useful would be a quantum equivalent of private-key cryptography\index{Private-key cryptography}, whereby a short key can be reused over and over again for different messages, meaning that only a short, shared secret-key would need to be established once-off (or at least very infrequently).

>>>>

\subsection{Private-key cryptography}\index{Private-key!Cryptography}

@@

Note that when performing a brute-force attack against a private encryption key\index{Private-key!Cryptography}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime, since \mbox{$O(\sqrt{2^k}) = O(2^{k/2})$}. Thus, in the quantum era private-key lengths will need to be doubled to maintain an equivalent level of security against brute-force attacks.

@@

The best known attack against photonically implemented BB84 is the `photon-number splitting attack'\index{Photon-number-splitting attacks}. This attack targets implementations where Alice's photon source does not produce perfect single-photon states, but may have some amplitude of higher photon-number. Weak coherent states or SPDC states exhibit this property. The attack is very simple. Eve simply performs a man-in-the-middle attack\index{Intercept-resend attacks}, but not of an intercept-resend\index{Intercept-resend attacks} variety. Rather than intercepting the entire channel, she inserts a low reflectivity beamsplitter and measures only the reflected mode, the other following its desired trajectory to Bob. Now there is a chance that Eve can extract just one of the multiple photons in the signal, such that Bob still receives a photon. Eve holds the split-off signal in memory until the classical communication of encoding bases, at which point she measures all her split signals in the correct basis, thereby recovering the associated secret-key bit.

@@

What would be more useful would be a quantum equivalent of private-key cryptography\index{Private-key!Cryptography}, whereby a short key can be reused over and over again for different messages, meaning that only a short, shared secret-key would need to be established once-off (or at least very infrequently).

### 2018-11-07 Sections/economics_of_the_quantum_internet.tex
More indexing

\subsection{Network growth} \index{Network growth}

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on a consistent exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point to this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N(t) = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

@@

\section{Network power}\index{Network power}\label{sec:network_power}

@@

\begin{postulate}[Network power]\label{post:network_power}\index{Network power}
The combined computational power of the entire network, measured in classical-equivalent runtime (i.e FLOPs), is given by,
\begin{align}
P(t) &= f_\mathrm{sc}(n_\mathrm{global})\nonumber \\
&= f_\mathrm{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

@@

\section{Network value}\index{Network value}\label{sec:network_value}

@@

\begin{postulate}[Network value]\label{post:network_value}\index{Network value}
The dollar-value of the entire network is given by,
\begin{align}
	V(t) &= C(t) N(t) \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

@@

\section{Problem size scaling functions}\index{Problem size scaling functions}\label{sec:prob_sc_func}

@@

\begin{definition}[Problem size scaling function]\index{Problem size scaling functions}
The problem size scaling function relates the size of a problem instance ($s$), in some arbitrary metric, to its classical-equivalent runtime ($t$) under a time-shared network model,
\begin{align}
t = f_\mathrm{size}(s).
\end{align}
Equating this with the time-shared computational power yields,
\begin{align}
	n\cdot \chi_\mathrm{sc}(n_\mathrm{global}) = f_\mathrm{size}(s).
\end{align}
Isolating the problem size yields,
\begin{align}
s = f_\mathrm{size}^{-1}(n\cdot \chi_\mathrm{sc}(n_\mathrm{global})).
\end{align}
\end{definition}

@@

Much like the classical internet, it's to be expected the network that will emerge will approximate a scale-free network (Sec.~\ref{sec:scale_free_networks})\index{Scale-free networks}, with a very hierarchical structure, following a Pareto distribution\index{Pareto distribution} in hub-size.

>>>>

\subsection{Network growth} \index{Network!Growth}

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on a consistent exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point to this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network!Growth}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N(t) = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

@@

\section{Network power}\index{Network!Power}\label{sec:network_power}

@@

\begin{postulate}[Network power]\label{post:network_power}\index{Network!Power}
The combined computational power of the entire network, measured in classical-equivalent runtime (i.e FLOPs), is given by,
\begin{align}
P(t) &= f_\mathrm{sc}(n_\mathrm{global})\nonumber \\
&= f_\mathrm{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

@@

\section{Network value}\index{Network!Value}\label{sec:network_value}

@@

\begin{postulate}[Network value]\label{post:network_value}\index{Network!Value}
The dollar-value of the entire network is given by,
\begin{align}
	V(t) &= C(t) N(t) \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

@@

\section{Problem size scaling functions}\index{Problem size!Scaling functions}\label{sec:prob_sc_func}

@@

\begin{definition}[Problem size scaling function]\index{Problem size!Scaling functions}
The problem size scaling function relates the size of a problem instance ($s$), in some arbitrary metric, to its classical-equivalent runtime ($t$) under a time-shared network model,
\begin{align}
t = f_\mathrm{size}(s).
\end{align}
Equating this with the time-shared computational power yields,
\begin{align}
	n\cdot \chi_\mathrm{sc}(n_\mathrm{global}) = f_\mathrm{size}(s).
\end{align}
Isolating the problem size yields,
\begin{align}
s = f_\mathrm{size}^{-1}(n\cdot \chi_\mathrm{sc}(n_\mathrm{global})).
\end{align}
\end{definition}

@@

Much like the classical internet, it's to be expected the network that will emerge will approximate a scale-free network (Sec.~\ref{sec:scale_free_networks})\index{Scale-free networks}, with a very hierarchical structure, following a Pareto distribution\index{Power law} in hub-size.

### 2018-11-07 Sections/essay_the_economics_of_the_quantum_internet.tex
More indexing

\dropcap{Q}{uantum} computers are highly likely to, at least initially, be extremely expensive, and affordable outright by few. Client/server economic models based on outsourcing\index{Outsourced quantum computation} of computations to servers on a network, will be essential to making quantum computing widely accessible. The protocols we have presented here pave the way for this type of economic model to emerge. It is paramount that the types of technologies introduced here be fully developed in time for the deployment of useful quantum computing hardware, such that they can be fully commercialised from day one of their availability, enabling widespread adoption, enhanced economy of scale, and rapid proliferation.

@@

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just a few years ago would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience'\index{IBM Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

>>>>

\dropcap{Q}{uantum} computers are highly likely to, at least initially, be extremely expensive, and affordable outright by few. Client/server economic models based on outsourcing\index{Outsourced!Quantum computation} of computations to servers on a network, will be essential to making quantum computing widely accessible. The protocols we have presented here pave the way for this type of economic model to emerge. It is paramount that the types of technologies introduced here be fully developed in time for the deployment of useful quantum computing hardware, such that they can be fully commercialised from day one of their availability, enabling widespread adoption, enhanced economy of scale, and rapid proliferation.

@@

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced!Quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just a few years ago would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience'\index{IBM Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

### 2018-11-07 Sections/essay_the_quantum_space_race.tex
More indexing

To facilitate a true global network, next-generation satellites\index{Next-generation quantum satellites} will need to form a constellation\index{Constellation network} sufficiently dense that every point on the Earth's surface is always within line of sight of at least one satellite (Fig.~\ref{fig:sat_honeycomb}).

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{satellite_honeycomb_lattice}
\captionspacefig \caption{A honeycomb lattice\index{Honeycomb lattice} is the lowest order two-dimensional lattice that could be employed to construct a satellite constellation\index{Constellation network} network covering the Earth. Edges represent quantum communications channels, and their intersections are where the satellites reside. Such a network will require next-generation satellites\index{Next-generation quantum satellites} with satellite-to-satellite links.}\label{fig:sat_honeycomb}	
\end{figure}

@@

A global constellation network\index{Constellation network} may require hundreds or thousands of individual satellites. The key to deploying such a network will be via economies of scale\index{Economies of scale}. We must design a single standardised satellite (for example along the lines of that shown in Fig.~\ref{fig:next_gen_sat}), rather than a variety of more specialised models, make it as minimalistic as possible, and then mass produce them on a large scale. With this approach we can hope for economical deployment of a true space-based point-to-point\index{Point-to-point network} global network.

>>>>

To facilitate a true global network, next-generation satellites\index{Next-generation!Quantum satellites} will need to form a constellation\index{Constellation network} sufficiently dense that every point on the Earth's surface is always within line of sight of at least one satellite (Fig.~\ref{fig:sat_honeycomb}).

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{satellite_honeycomb_lattice}
\captionspacefig \caption{A honeycomb lattice\index{Honeycomb lattice} is the lowest order two-dimensional lattice that could be employed to construct a satellite constellation\index{Constellation network} network covering the Earth. Edges represent quantum communications channels, and their intersections are where the satellites reside. Such a network will require next-generation satellites\index{Next-generation!Quantum satellites} with satellite-to-satellite links.}\label{fig:sat_honeycomb}	
\end{figure}

@@

A global constellation network\index{Constellation network} may require hundreds or thousands of individual satellites. The key to deploying such a network will be via economies of scale\index{Economies of scale}. We must design a single standardised satellite (for example along the lines of that shown in Fig.~\ref{fig:next_gen_sat}), rather than a variety of more specialised models, make it as minimalistic as possible, and then mass produce them on a large scale. With this approach we can hope for economical deployment of a true space-based point-to-point\index{Point-to-point (P2P)!Network} global network.

### 2018-11-07 Sections/essay_to_the_future_QKD.tex
More indexing

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellite-to-ground links}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Secret-keys} for private-key cryptography\index{Private-key cryptography} with guaranteed key secrecy.

@@

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication\index{Point-to-point communication}, but have implications for a range of network applications, such as quantum secret sharing\index{Quantum secret sharing} \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing\index{Blind quantum computation} \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting\index{Quantum anonymous broadcasting} \cite{bib:christandl2005quantum}, and many more.

>>>>

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellite-to-ground links}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Secret-keys} for private-key cryptography\index{Private-key!Cryptography} with guaranteed key secrecy.

@@

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication\index{Point-to-point (P2P)!Communication}, but have implications for a range of network applications, such as quantum secret sharing\index{Quantum secret sharing} \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing\index{Blind quantum computation} \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting\index{Quantum anonymous broadcasting} \cite{bib:christandl2005quantum}, and many more.
